j_play

### 2020-12-03 scripts/BCOR_combo.Rmd
Trying to Update Again
ES data calculated for Rural vs. Urban Settings

ESdata <- BCdatastripped %>% 
  filter(SPECIAL_NEEDS_CODE == "High Behavioural Need",
         DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School",
         DISTRICT_NUMBER == "036")  %>% 
  mutate(Public_population = BCpopulation$TOTAL_ENROLMENT[SCHOOL_YEAR-8],
         prevalence = NUMBER_OF_STUDENTS/Public_population) %>% 
  mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995,
         pre16 = ifelse(SCHOOL_YEAR <= 2016, "before16", "after16")) %>%
  group_by(pre16) %>% 
  pivot_wider(
    names_from = pre16,
    values_from = prevalence
  )

presup <- ESdata %>% 
  drop_na(before16) %>% 
  select(before16)
as.numeric(unlist(presup))

postsup <- ESdata %>% 
  drop_na(after16) %>% 
  select(after16)
as.numeric(unlist(postsup))

@@

esc_mean_sd(grp1m = presup_mean, grp1sd = presup_sd, grp1n = 13, grp2m = postsup_mean, grp2sd = postsup_sd, grp2n = 3, es.type = "g")

>>>>

urban <- c("023", "034", "035", "036", "037", "038", "039", "040", "041", "042", "043", "044", "045", "046")

ESdata <- BCdatastripped %>% 
  filter(SPECIAL_NEEDS_CODE == "Chronic Health",
         DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School",
         !DISTRICT_NUMBER %in% urban)  %>% 
  mutate(Public_population = BCpopulation$TOTAL_ENROLMENT[SCHOOL_YEAR-8],
         prevalence = NUMBER_OF_STUDENTS/Public_population) %>% 
  mutate(SCHOOL_YEAR = SCHOOL_YEAR+1995,
         pre16 = ifelse(SCHOOL_YEAR <= 2016, "before16", "after16")) %>%
  group_by(pre16) %>% 
  pivot_wider(
    names_from = pre16,
    values_from = prevalence
  )

presup <- ESdata %>% 
  drop_na(before16) %>% 
  select(before16)
as.numeric(unlist(presup))
presup_count <- count(presup)

postsup <- ESdata %>% 
  drop_na(after16) %>% 
  select(after16)
as.numeric(unlist(postsup))
postsup_count <- count(postsup)

@@

esc_mean_sd(grp1m = presup_mean, grp1sd = presup_sd, grp1n = presup_count, grp2m = postsup_mean, grp2sd = postsup_sd, grp2n = postsup_count, es.type = "g")
